%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 2.0 (15/4/2019)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
% With extensive modifications by:
% Gabriel Urbain (gabriel.urbain@ugent.be)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[a4paper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

% % Coordinates
% Comment this line for blinding the coordinates
\def\notblinded{}

\ifdefined\notblinded
\def\name{Gabriel}
\def\surname{Urbain}
\def\description{I am a PhD engineer student with a background in Electronics, Computer Sciences and Aerospace. I am looking for a R\&D position in company specialized in advanced robotics, using state-of-art perception, computation and actuation techniques. I fancy challenging projects with a high societal, economical and environmental impact where I can fully invest my passion and time.}
\def\address{23, Onafhankelijkheidslaan \hspace{5pt} 9000 Gent \hspace{5pt} Belgium}
\def\website{\url{http://gurbain.be/}}
\def\email{\url{gabriel.urbain@ugent.be}}
\def\phone{(+32) 484 102088}
\else
\def\name{Urbain}
\def\surname{Gabriel}
\def\description{I am a PhD engineer student with a background in Electronics, Computer Sciences and Aerospace. I am looking for a R\&D position in company specialized in advanced robotics, using state-of-art perception, computation and actuation techniques. I fancy challenging projects with a high societal, economical and environmental impact where I can fully invest my passion and time.}
\def\address{Address}
\def\website{\url{Website}}
\def\email{\url{E-mail}}
\def\phone{Phone}
\fi


\begin{document}

%----------------------------
%	TITLE SECTION
%----------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{\name}{\surname}{\description}{ % Your name
\newline\address\\
\website \hspace{5pt} | \hspace{5pt} \email \hspace{5pt} | \hspace{5pt} \phone % Your contact information
}

\sectionspace % Some whitespace after the section
%----------------------------
%	FIRST PAGE
%----------------------------
\vspace{4pt}

\section{Experience}
\vspace{5pt}
\runsubsection{UGent}
\descript{| \hspace{2pt} PhD Student - Research Assistant at AIRO Group, IDLab - imec}
\location{October 2015 - Present | Gent, Belgium}
Topic: \textit{Locomotion of compliant quadruped robots at the crossing of AI and Neurosciences.} Human Brain Project. Neurorobotics branch ({\url{http://neurobotics.net/}). \runparagraph{Main topics}: compliant robotics, locomotion, central pattern generators, supervised learning, reinforcement learning, artificial neural networks, spiking neural networks, automation. \\
\runparagraph{Doctoral schools}: machine learning, auditory perception and computation, 3D modeling, career building, English presentation skills. \\
\runparagraph{Teaching Assistant}: embedded prototyping - industrial engineers campus Kortrijk (2016), digital electronics - FPGA programming class (2016-2018), robotics - labs and project (2018)
\vspace{9pt}

%------------------------------------------------

\runsubsection{Italian Institute of Technology}
\descript{| \hspace{2pt} Visiting PhD Reseacher}
\location{July - October 2018 | Genoa, Italy}
Topic: \textit{Machine Learning for low-level locomotion on the HyQ robot}. Dynamic Legged Systems Lab.

\vspace{9pt}
%------------------------------------------------

\runsubsection{UMons}
\descript{| \hspace{2pt} Researcher at the numediart Institute}
\location{February - October 2015 | Mons, Belgium}
Topic: \textit{Development of a Search Engine Based on Audio Similarities for Large Collections of Foley Sounds.} Research in partnership with Dame Blanche SA and CETIC.

\vspace{9pt}
%------------------------------------------------

\runsubsection{Thales Alenia Space}
\descript{| \hspace{2pt} Research and Innovation Internship}

\location{August - September 2013 | Charleroi, Belgium}
Topic: \textit{Feasibility Analysis of an Electro-Mechanical Control System for Ariane Rocket Boosters}.

\vspace{9pt}
%------------------------------------------------

\runsubsection{UMONS}
\descript{| \hspace{2pt} Research Initiation Internship}
\location{July - August 2011 | Mons, Belgium}
Topic: \textit{Semi-Automatic Creation of a 3D Model for the City of Mons}.

\vspace{9pt}
%------------------------------------------------

\runsubsection{UMONS}
\descript{| \hspace{2pt} Research Initiation Internship}
\location{July - August 2010 | Mons, Belgium}
Topic: \textit{Implementation of C/C++ Libraries in TRNSYS 16.1 for Heat Pump Study}.

\vspace{14pt}

%------------------------------------------------
% Formation
%------------------------------------------------

\section{Education}
\vspace{5pt}

\runsubsection{Massachusetts Institute of Technology\\}
\vspace{2pt}
\descript{Master Thesis at the Space Systems Laboratory}
\location{June 2014 – November 2014 | Cambridge, USA}
Topic: \textit{Calibration and Fusion of Stereoscopic and Time-of-Flight Cameras for Zero Gravity Targets Inspection}. Passed with the highest mention.

\vspace{9pt}
%------------------------------------------------

\runsubsection{ISAE | SUPAERO\\}
\vspace{2pt}
\descript{Master of Science in AeroSpace Engineering}
\location{August 2012 – November 2014 | Toulouse, France}
Double Master Degree trough \textit{T.I.M.E.} Network. Major : Space Systems, Telecommunications and Networks.

\vspace{9pt}
%------------------------------------------------

\runsubsection{UMONS | Faculté Polytechnique\\}
\vspace{2pt}
\descript{Master of Science in Electrical Engineering}
\location{September 2011 – November 2014 | Mons, Belgium}
Major: Multimedia et Telecommunications. Graduated with Honors.

\vspace{3pt}
\descript{Bachelor of Science in Engineering}
\location{September 2008 – June 2011 | Mons, Belgium}
Major: Electricity and Electronics. Graduated with Honors.

%----------------------------
%	SECOND PAGE
%----------------------------
\pagebreak
\vspace*{0.1pt}

\begin{minipage}[b]{0.55\linewidth}
	
	%------------------------------------------------
	% Patents
	%------------------------------------------------
	
	\section{Patents}
	
	\vspace{5pt}
	\textbf{Audio Search User Interface}.\\
	\textbf{G. Urbain}, A. Moinet, C. Frisson. Pending with registry number EP3430535. \textit{European Patent Office}. 2017
	
	\vspace{18pt}
	
\end{minipage}
\hfill
\begin{minipage}[b]{0.42\linewidth}
	
	%------------------------------------------------
	% Language
	%------------------------------------------------
	
	\section{Languages}
	\vspace{5pt}
	\noindent
	\textbf{French  \tabto{1.5cm} | \hspace{2pt}} Native. C2\\
	\textbf{English   \tabto{1.5cm}| \hspace{2pt}}  Fluent. C1. TOEFL IBT 105/120 in 2014\\
	\textbf{Dutch  \tabto{1.5cm} | \hspace{2pt}}  Professional. B2\\
	\textbf{Spanish  \tabto{1.5cm} | \hspace{2pt}} Basic. A2\\
	\textbf{Italian  \tabto{1.5cm}| \hspace{2pt}}  Basic. A1
	
\end{minipage}

\vspace{10pt}

\begin{minipage}[b]{0.53\linewidth}
	%------------------------------------------------
	% Conf, workshops
	%------------------------------------------------
	
	\section{Workshops -  Symposiums}
	
	\vspace{5pt}
	\textbf{4th HBP School | Future of Artificial Intelligence} \\
	Lightning talk and poster session. June 2017, Obergurgl, Austria.
	
	\vspace{5pt}
	\textbf{1st Neurorobotics Platform User Workshop} \\
	April 2017, Munich, Germany.
	
	\vspace{5pt}
	\textbf{3rd HBP School | Future of Neuroscience} \\
	Lightning talk and poster session. December 2016, Obergurgl, Austria.
	
	\vspace{5pt}
	\textbf{Let's Talk Science! | Communication Summer School} \\
	PhD thesis presentation in a one man show fashion. July 2016. Gent, Belgium.
	\vspace{5pt}
	
	\textbf{4th HBP Education Workshop | Future of Computing} \\
	Lightning talk and poster session. January 2016. Manchester, UK.
	
	\vspace{5pt}
	\textbf{5th Cubesat Symposium and the 6th QB50 Workshop} \\
	Lightning talk and poster session. June 2013. Brussels, Belgium.
	
	\vspace{5pt}
\end{minipage}
\hfill
\begin{minipage}[b]{0.42\linewidth}
			
	%------------------------------------------------
	% Skills
	%------------------------------------------------
	
	\section{Skills}
	\vspace{5pt}
	\subsection{IT and Software}
	\vspace{2pt}
	\location{Operating Systems | Middleware}
	Linux \textbullet{} Embedded Linux \textbullet{} Windows \textbullet{} ROS \textbullet{} Docker\\
	\vspace{3pt}
	\location{Languages}
	C \textbullet{} C++ \textbullet{} Python \textbullet{} Matlab \textbullet{} Java \textbullet{} Bash \textbullet{} VHDL \textbullet{} OpenCV \textbullet{} Git \textbullet{} \LaTeX\\
	\vspace{3pt}
	\location{Embedded Platforms}
	Low-level development on: X86 \textbullet{} Atmel AVR (Arduinos, self-designed boards) \textbullet{} ARM (BeagleBone, RaspberryPI, Odroid) \textbullet{} Neuromorphic Hardware (SpiNNaker, BrainScaleS)
	\vspace{5pt}
	
	\subsection{Technical}
	Embedded Systems \textbullet{}
	Image and Audio Processing \textbullet{} Neural Networks \textbullet{} Machine Learning \textbullet{} Robotics \textbullet{} Electronics \textbullet{} Telecommunications \textbullet{} Space Systems
	\vspace{5pt}
\end{minipage}

\vspace{10pt}


%------------------------------------------------
% Publications
%------------------------------------------------

\section{Publications}
\vspace{5pt}

\textbf{Body Randomization Reduces the Sim-to-Real Gap for Compliant Quadruped Locomotion}. \\
A. Vandesompele, \textbf{G. Urbain}, H. Mahmud,  F. wyffels and J. Dambre.
In \textit{Frontiers in Neurorobotics 13, 9}. 2019

\vspace{5pt}
\textbf{Calibration Method to Improve Transfer from Simulation to Quadruped Robots}. \\
\textbf{G. Urbain}, A. Vandesompele, F. wyffels and J. Dambre.
\textit{International Conference on Simulation of Adaptive Behavior, 102-113}. 2018

\vspace{5pt}
\textbf{Design of a Bio-inspired Compliant Quadruped Robot for Research on Closed-Loop Locomotion Control}.\\
\textbf{G. Urbain}, A. Vandesompele, F. wyffels and J. Dambre.
\textit{2nd HBP Student Conference: Transdisciplinary Research Linking Neuroscience, Brain Medicine and Computer Science}. 2018

\vspace{5pt}
\textbf{Morphological Properties of Mass-Spring Networks for Optimal Locomotion Learning}. \\
\textbf{G. Urbain}, J. Degrave, B. Carette, F. wyffels and J. Dambre. In \textit{Frontiers in Neurorobotics}. 2017

\vspace{5pt}
\textbf{A Semantic and Content-Based Search User Interface for Browsing Large Collections of Foley Sounds}. \\
\textbf{G. Urbain}, C. Frisson, A. Moinet and T. Dutoit. In: \textit{Audio Mostly - A conference on interaction with sound}. 2016

\vspace{5pt}
\textbf{INSPECT Sensor Suite for On-Orbit Inspection and Characterization with Extravehicular Activity Spacecraft}.\\
D. Steinberg, T. Sheerin and \textbf{G. Urbain}.
\textit{45th International Conference on Environmental Systems}. 2015

\vspace{15pt}

%------------------------------------------------
% Organizations
%------------------------------------------------

\section{Other Positions}
\vspace{5pt}
\begin{minipage}[b]{0.71\linewidth}
	\runsubsection{Human Brain Project (HBP)}
	\descript{| \hspace{2pt} Student Representative}
	\location{2016 - Present | Innsbruck, Austria}
	Student ambassador in the HBP Neurorobotics branch (2016, 2017) and elected Student Representative at the HBP Education Programme Committee until May 2019.
	
	\vspace{12pt}
	
	%------------------------------------------------
	
	\runsubsection{iRobotique}
	\descript{| \hspace{2pt} Administrator}
	\location{2004 - Present | Mons, Belgium}
	Class on electronics, microprocessor programming and robotic design. Participation to Eurobot Junior (2005, 2006, 2008) and Eurobot (2011, 2013) with multiple rewards: Creativity Award (2006), Belgian Junior Champions Award (2008), 8th European Junior position (2008), 7th European position (2013). Design and development of robotic platform for museum guided tours since 2014.
	
	\vspace{12pt}
	
	%------------------------------------------------
	
	\runsubsection{Museomix Belgium}
	\descript{| \hspace{2pt} Administrator and Organiser}
	\location{2015 - Present | Brussels, Belgium}
	Organization of hackatons and events confronting people from technological and cultural backgrounds to define the future of museum mediation in Belgium. Communication and website manager.
	
\end{minipage}
\hfill
\begin{minipage}[b]{0.28\linewidth}
	\runsubsection{Hobbies}
	\\ [5pt]
	\noindent
	Gent University Symphonic Orchestra (2016-present) \textbullet{} Gent Alumni and Staff Orchestra (2017-present) \textbullet{}  Sailing (2014) \textbullet{}  CubeSat (2012-2014) \textbullet{} Scuba Diving (2013-2014) \textbullet{} Supaero Jazz Band (2012-2014) \textbullet{} Rowing (2013) \textbullet{} Winner of a GDF Suez scholarship (2012)  \textbullet{} Student Regional Committee (2009-2012) \textbullet{} Board of Faculty (2011-2012)  \textbullet{} \textbullet{} Commission of Academic Program Evaluation (2011-2012) \textbullet{}  Board of Libraries (2010-2011) \textbullet{} Student Culture Committee (2010-2011) \textbullet{} Jazz Band Baudour (2001-2011) \textbullet{} Drums \textbullet{} Trumpet \textbullet{} Piano \textbullet{} Choral
\end{minipage}

%------------------------------------------------




\end{document}